Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
Clarify experimental procedure

\noindent {\bfseries Experiment Logistics} 
The IRB protocol to run this user study has been approved (2014-12-6995). 
We plan to recruit from 100-200 users for the purpose of this study, 
making it largest user study to examine Tor.  This study will be conducted at the 
Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley, which consists of 36 laptops with 
cubicle walls separating each laptop. We will use individual host firewalls to simulate
censorship environments and will record computer screens to capture 
user activity. The total length of the experiment, including briefing, completing the censorship 
circumvention tasks, exit survey, and debriefing, will take about an hour. 
Participants will be compensated \$30 for their time, which is more to cover 
minimum wage for an hour and any transportation costs to the lab.  \\

\noindent {\bfseries Experiment Flow} 
We start off the experiment by telling them that they are in an adversarial
setting, and that some websites are blocked and some websites are not. We will
instruct them to visit a non-blocked website and a blocked website on a
``standard'' browser (one that is not used for censorship circumvention, such
as Chrome, Safari, or Firefox) to illustrate the situation.
Then, the participants will be informed of the role they they will be playing in the study. Particularly,
they will be informed that they are a normal citizen in a censorship environment
which prevents them from visiting certain websites, that they are visiting the website for non-critical leisurely purposes,
and that there is a minimal chance of risk. This information is given so that
the participants can have an idea of the role they are playing, and to achieve
consistency across participants. Their behavior might be different if they were
visiting websites to accomplish a critical task, or if they knew that there
were great risks.

After explaining the situation and their role, we will explain what Tor is, and
how they can use it if necessary, and instruct them to complete the a set of
tasks which will require visiting blocked websites. Ultimately, the
participants will need to configure their Tor Browser to circumvent the
simulated censorship environment. These tasks have a three-fold purpose of
providing participants with feedback (if they did not correctly configure their
browser, they cannot reach the website),  motivating the participants to
configure the browser correctly, and providing the researchers with an
indicator of successful censorship circumvention. While participants are on the
computer, their screens will be recorded to capture how participants configure
their browser, and to provide additional evidence that they have completed the
tasks. The participants will be unaware that their screens are being recorded,
to prevent deviations in behavior.

After completing the browsing tasks, we will administer a survey that 1)
measures participant demographics, participant technical fluency, and
participant familiarity with Tor and 2) collects qualitative feedback on from
participants on their browsing experience, particularly with respect to any
parts of the configuration interface which was confusing to them, but also
about the browsing experience as a whole.  A rough draft of the survey can be
found
\href{http://www.surveygizmo.com/collab/2085559/Tor-Usability-Survey}{here}.

>>>>

\noindent {\bfseries Experiment Logistics} 
The IRB protocol to run this user study has been approved (2014-12-6995). 
We plan to recruit from 100-200 users for the purpose of this study, 
making it the largest user study of Tor to date.  This study will be conducted at the
Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley, which consists of 36 laptops,
separated by cubicle walls. We will use individual host firewalls to simulate
censorship environments and will record computer screens to capture 
user activity. The total length of the experiment, including briefing, completing the censorship 
circumvention tasks, exit survey, and debriefing, will be about an hour.
Participants will be compensated \$30 for their time, which covers
minimum wage for an hour and any transportation costs to the lab.  \\

\noindent {\bfseries Experiment Flow} 
The experiment begins with the participants being informed that they are in a
simulated censorship
environment, where some --- but not all --- websites are blocked. We will
instruct them to visit a non-blocked website and a blocked website on a
``standard'' browser (one that is not used for censorship circumvention, such
as Chrome, Safari, or Firefox) to illustrate the situation.
Then, the participants will find out the role they they will be playing in the study.
This role is that of a regular citizen, who is trying to visit blocked websites
for non-critical leisurely purposes,
and that there is a minimal chance of risk. This information is given
to achieve
consistency across participants: their behavior might be different if they were
visiting websites to accomplish a critical task, or if they knew that there
were great risks.

After explaining the situation and their role, we will explain what Tor is, and
how they can use it if necessary, and instruct them to complete a set of
tasks which will require visiting blocked websites. Ultimately, the
participants will need to configure their Tor Browser to circumvent the
simulated censorship environment. These tasks have a three-fold purpose of
providing participants with feedback (if they did not correctly configure their
browser, they cannot reach the website),  motivating the participants to
configure the browser correctly, and providing the researchers with an
indicator of successful censorship circumvention.
Participants' screens will be recorded to capture how they configure
their browser, and to provide additional evidence that they have completed the
tasks.

After users complete the browsing tasks, we will administer a survey that 1)
measures demographics, technical fluency, and
familiarity with Tor and 2) collects qualitative feedback from
participants about their browsing experience as a whole
and the configuration interface specifically.
A rough draft of the survey can be
found
\href{http://www.surveygizmo.com/collab/2085559/Tor-Usability-Survey}{here}.
